MSDS_6372_Project2

### 2022-07-28 MSDS_6372_Project2.Rmd
mostly complete code

#### Loading the necessary R libraries for the analysis
```{r message = FALSE}
# Load the necessary libraries
library(knitr)
library(rmarkdown)
# From class
library(GGally)
library(epitools)
library(MASS)
library(tidyverse)
library(car)
library(caret)
library(glmnet)
library(ROCR)
library(pROC)
#Dasta set
library(aplore3)
library(ResourceSelection)

@@

>>>>

#### Loading the necessary R libraries for the analysis
```{r message = FALSE}
# Load the necessary libraries
library(knitr)
library(rmarkdown)
# From class
library(GGally)
library(epitools)
library(MASS)
library(tidyverse)
library(car)
library(caret)
library(glmnet)
library(ROCR)
library(pROC)
library(rpart)
library(rpart.plot)
library(rattle)
#Dasta set
library(aplore3)
library(ResourceSelection)

@@

#####################################################################################
#                                        LDA/QDA                                    #
#####################################################################################
```{r, LDA QDA}
# LDA
lda.train = train[,-16]
lda.test = test[,-16]

lda.model = lda(fracture ~age+weight+height+bmi+fracscore, prior = c(.75, .25), data = lda.train)
plot(lda.model)

lda.model.pred.train = predict(lda.model, lda.train)
lda.model.pred.test = predict(lda.model, lda.test)

# LDA ROC cuve
lda.roc<-roc(response=lda.test$fracture,predictor=lda.model.pred.test$posterior[,2],levels=c("No","Yes"))
plot(lda.roc,print.thres="best")

cutoff.lda = 0.291
lda.pred.adj.train = ifelse(lda.model.pred.train$posterior[,2] > cutoff.lda, "Yes", "No")
lda.pred.adj.test = ifelse(lda.model.pred.test$posterior[,2] > cutoff.lda, "Yes", "No")

# LDA Confusion matrix
confusionMatrix(table(lda.pred.adj.train,lda.train$fracture), positive = "Yes")
confusionMatrix(table(lda.pred.adj.test,lda.test$fracture), positive = "Yes")

#Scoring
lda.prob.test = predict(lda.model, lda.test, type = "prob")
AUC = auc(lda.test$fracture, lda.prob.test$posterior[,2])
print(paste("Area Under the Cuve: ", AUC))

# QDA
qda.train = train[,-16]
qda.test = test[,-16]

qda.model = qda(fracture ~age+weight+height+bmi+fracscore, prior = c(.75, .25), data = qda.train)
plot(lda.model)

qda.model.pred.train = predict(qda.model, qda.train)
qda.model.pred.test = predict(qda.model, qda.test)

# QDA ROC cuve
qda.roc<-roc(response=qda.test$fracture,predictor=qda.model.pred.test$posterior[,2],levels=c("No","Yes"))
plot(qda.roc,print.thres="best")

cutoff.qda = 0.377
qda.pred.adj.train = ifelse(qda.model.pred.train$posterior[,2] > cutoff.qda, "Yes", "No")
qda.pred.adj.test = ifelse(qda.model.pred.test$posterior[,2] > cutoff.qda, "Yes", "No")

# QDA Confusion matrix
confusionMatrix(table(qda.pred.adj.train,qda.train$fracture), positive = "Yes")
confusionMatrix(table(qda.pred.adj.test,qda.test$fracture), positive = "Yes")

#Scoring
qda.prob.test = predict(qda.model, qda.test, type = "prob")
AUC = auc(qda.test$fracture, qda.prob.test$posterior[,2])
print(paste("Area Under the Cuve: ", AUC))

#####################################################################################
#                                   Decision Tree                                   #
#####################################################################################
```{r, decision tree}

dt.train = train[,-16]
dt.test = test[,-16]
#dt.train.dummy = model.matrix(fracture~., dt.train)

cv.dtree <- trainControl(
  method = "cv", 
  number = 5,
  savePredictions = TRUE,
  classProbs = TRUE,
  summaryFunction = twoClassSummary
)

dtree.model = train(
  fracture ~ ., 
  data = dt.train, 
  method = "rpart",
  metric = "ROC",
  tuneGrid = expand.grid(cp=0.0048),
  trControl=cv.dtree,
  tuneLength = 100
  )

# print the tree
fancyRpartPlot(dtree.model$finalModel)
bestcp = dtree.model$finalModel$cptable[which.min(dtree.model$finalModel$cptable[,"rel error"]),"CP"]
print(paste("Best complexity score: ", bestcp))

# Predicting
dtree.model.pred.train = predict(dtree.model, dt.train, type = "prob")
dtree.model.pred.test = predict(dtree.model, dt.test, type = "prob")

# ROC Curve 
dtree.roc<-roc(response=qda.test$fracture,predictor=dtree.model.pred.test$Yes,levels=c("No","Yes"))
plot(dtree.roc,print.thres="best")

cutoff.dtree = 0.138
dtree.pred.adj.train = ifelse(dtree.model.pred.train$Yes > cutoff.dtree, "Yes", "No")
dtree.pred.adj.test = ifelse(dtree.model.pred.test$Yes > cutoff.dtree, "Yes", "No")

# Confusion matrix
confusionMatrix(table(dtree.pred.adj.train,dt.train$fracture), positive = "Yes")
confusionMatrix(table(dtree.pred.adj.test,dt.test$fracture), positive = "Yes")

#Scoring
dt.prob.test = predict(dtree.model, dt.test, type = "prob")
AUC = auc(dt.test$fracture, dt.prob.test$Yes)
print(paste("Area Under the Cuve: ", AUC))
```
